---
title: "Dataset Overview"
author: "Matt Brousil"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

<br>

## **Variable definitions**

<br>

The `ticks_w_weather` dataset contains the following variables:

+ **`site_id`**: The four-letter NEON site code
+ **`date`**: The first day of the [MMWR week](https://www.cdc.gov/mmwr/index.html) for this row
+ **`jd`**: The Julian date calculated from the `date` column  
+ **`mmwr_year`**: The year of the MMWR week
+ **`mmwr_week`**: The week number of the MMWR week
+ **`mean_temp`**: The mean temperature of the current MMWR week. Calculated by taking the mean of daily mean temperatures
+ **`min_temp`**: The minimum temperature of the current MMWR week. Calculated by taking the minimum of daily minimum temperatures
+ **`max_temp`**: The maximum temperature of the current MMWR week. Calculated by taking the maximum of daily maximum temperatures
+ **`mean_rh`**: The mean relative humidity (%) of the current MMWR week. Calculated by taking the mean of daily mean RH values
+ **`rh_min`**: The minimum relative humidity (%) of the current MMWR week. Calculated by taking the minimum of daily minimum RH values
+ **`rh_max`**: The maximum relative humidity (%) of the current MMWR week. Calculated by taking the maximum of daily maximum RH values
+ **`mean_vpd`**: The mean vapor pressure deficit for the current MMWR week. Calculated by taking the mean of daily mean VPD values
+ **`mean_precip_mm`**: The mean daily precipitation (mm) for the current MMWR week. Calculated by taking the mean of daily precipitation sums
+ **`sum_precip_mm`**: Sum of daily precipitation (mm) for the current MMWR week. Calculated by summing the daily precipitation sums
+ **`dd`**: The average daily degree days accumulated over the current MMWR week
+ **`thirty_day_dd`**: The mean 30-day-rolling-sum of degree days for the current MMWR week. Calculated by taking the mean of daily thirty-day rolling sums
+ **`dd_30d_rollsum_lag34`**: The mean 30-day-rolling-sum of degree days for the MMWR week 34 weeks previous. To calculate: 1) Get `thirty_day_dd` calculations, 2) get the 34-week lagged values of those (i.e., `lag(x = thirty_day_dd, n = 34L)`), 3) average the values for all days in the current MMWR week
+ **`dd_30d_rollsum_lag42`**: Same as `lag_thirty_day_dd_34wk`, but 42 weeks previous
+ **`dd_30d_rollsum_lag50`**: Same as `lag_thirty_day_dd_34wk`, but 50 weeks previous
+ **`dd_30d_rollsum_prev_week`**: This is the thirty-day rolling sum of degree days from the *last day* of the previous MMWR week. No averaging takes place. e.g, if today is Sunday, then this is the 30-day rolling degree day sum of yesterday (Saturday)
+ **`cume_dd_prev_week`**: Similar to `dd_30d_rollsum_prev_week`, except this is the cumulative degree day count (*starting Jan. 1*) of the the last day of the previous MMWR week
+ **`cume_cd_prev_winter`**: The total number of "chill days" (see method below under *Notes*) from September 1st of the preceding year to March 31st of the current year. Values before April 1st use the previous year's accumulations
+ **`amblyomma_americanum`**: The density of *Amblyomma americanum* ticks for the current MMWR week, reported as ticks per 1600m^2^ 
+ **`amam_filled`**: A version of the tick count column above that has been gap filled using linear interpolation
+ **`tick_interp_flag`**: A flag column that indicates whether the week's value for `amam_filled` was observed or interpolated
+ **`amam_4wk_rollmean_lag1`**: The four-week rolling average of the interpolated tick count column, then lagged by one week
+ **`mean_vpd_4wk_rollmean_lag1`**: The four-week rolling average of the `mean_vpd` column, then lagged by one week
+ **`amam_4wk_rollmean_lag50`**: The four-week rolling average of the interpolated tick count column, then lagged by 50 weeks
+ **`mean_vpd_4wk_rollmean_lag50`**: The four-week rolling average of the `mean_vpd` column, then lagged by 50 weeks

<br>

**Notes**:

+ *Degree days*: mean(min_temp, max_temp) - 0. Then, if the results is positive, this is the number of `degree days` accumulated that day. Negative values (i.e., temps below 0C) do not count towards this.
+ *Chill days* = 0 - mean(min_temp, max_temp). Then, if the result is positive, this is the number of `chill days` accumulated that day. Negative values (i.e., temps above 0C) do not count towards this. 



<br>

## **Dataset preview** 

```{r, echo=FALSE}
tar_read(interpolated_tick_data)$dataset %>%
  head(10) %>%
  kable() %>%
  kable_paper() %>% 
  scroll_box(width = "800px", height = "500px")
```

<br>

<br>

---

## **Quality control plots**

<br>

### **Missing data**:

```{r, echo=FALSE}
tar_read(tick_weather_missing_data_plot)$missing_plot
```

<br>

### **Variables vs. data source**:

<br>


#### **Minimum temp**

**Timeseries**

```{r, echo=FALSE}
tar_read(temperature_source_comparison_plots)$min_plot
```

**1:1**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
tar_read(one_to_one_plots)$min_temp_facet_plot +
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          title = element_text(size = 14),
          strip.text = element_text(size = 11),
          legend.position = "bottom")
```


<br>


#### **Maximum temp**

**Timeseries**

```{r, echo=FALSE}
tar_read(temperature_source_comparison_plots)$max_plot
```

**1:1**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
tar_read(one_to_one_plots)$max_temp_facet_plot +
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          title = element_text(size = 14),
          strip.text = element_text(size = 11),
          legend.position = "bottom")
```

<br>


#### **Minimum RH**

**Timeseries**

```{r, echo=FALSE}
tar_read(rh_source_comparison_plots)$min_plot
```

**1:1**
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
tar_read(one_to_one_plots)$min_rh_facet_plot +
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          title = element_text(size = 14),
          strip.text = element_text(size = 11),
          legend.position = "bottom")
```

<br>


#### **Maximum RH**

**Timeseries**

```{r, echo=FALSE}
tar_read(rh_source_comparison_plots)$max_plot
```

**1:1**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
tar_read(one_to_one_plots)$max_rh_facet_plot +
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          title = element_text(size = 14),
          strip.text = element_text(size = 11),
          legend.position = "bottom")
```


<br>


#### **VPD**

**Timeseries**

```{r, echo=FALSE}
tar_read(vpd_source_comparison_plot)$vpd_plot
```

**1:1**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
tar_read(one_to_one_plots)$vpd_facet_plot +
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          title = element_text(size = 14),
          strip.text = element_text(size = 11),
          legend.position = "bottom")
```

<br>


#### **Precip**

**Timeseries**

```{r, echo=FALSE}
tar_read(precipitation_source_comparison_plot)$precip_plot
```

**1:1**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=7}
tar_read(one_to_one_plots)$precip_facet_plot +
    theme(axis.text = element_text(size = 11),
          axis.title = element_text(size = 13),
          title = element_text(size = 14),
          strip.text = element_text(size = 11),
          legend.position = "bottom")
```


#### **Tick counts**

<br>


**Tick count line plot**:

```{r, echo=FALSE}
tar_read(interpolated_tick_timeseries_plots)$normal_plot
```

<br>


**Raw tick counts overlaid on interpolation**:

```{r, echo=FALSE}
tar_read(interpolated_tick_timeseries_plots)$color_coded_plot
```

<br>


#### **Chill days**

```{r, echo=FALSE}
tar_read(chill_day_timeseries_plot)$chill_plot
```

<br>


## **Workflow diagram**

```{r}
tar_visnetwork()
```
